Flatiron cleaning

### 2021-12-22 Rmd/rdi analysis.Rmd
Fix imputation

```{r library, include=FALSE}
library(drake)
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
```

@@

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
```

@@

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
            therapy == "Upfront Chemo") |
           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
            therapy == "Upfront Surgery")))
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**

@@

<!-- `r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.   -->
<!-- `r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.   -->

@@

<!-- `r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.   -->
<!-- I am removing these patients   -->

<!-- Patients left: -->
```{r}
Frontline <- Frontline %>%
  filter(is.na(switch_drugs))
```

@@

# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

@@

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

@@

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
<!-- RDI for paclitaxel is not a factor associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059). -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->

>>>>

```{r library, include=FALSE}
library(drake)
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

@@

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
```

@@

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((
    therapy == "Upfront Chemo" &
      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
  ) | (
    therapy == "Upfront Surgery" &
      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
  )
  )
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline_adjusted <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**

@@

@@

<!-- Patients left: -->
```{r}
Frontline_adjusted <- Frontline_adjusted %>%
  filter(is.na(switch_drugs))
```

@@

# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**

# Imputation for stagecat and debulking status

https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vitalstatus, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os"] <- 0
Pred
```

patientid is not used which is good. But SURGERYDATE IS NOT.
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
Pred
```

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

Do m = 30 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.30 that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m=30, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
Above results are exponentiated (imputed data).  
As a reminder before imputation results are :
```{r}
nonimp_cox_model
```

Complete the chemo data and merge with original
```{r}
imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)
```

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

### For Upfront Surgery
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vitalstatus, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os"] <- 0
Pred
```

patientid is not used which is good. But SURGERYDATE IS NOT
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
Pred
```

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

Do m = 10 (The max fmi = 0.099 that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m=10, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
Above results are exponentiated (imputed data).  
As a reminder before imputation results are :
```{r}
nonimp_cox_model
```

Complete the data and merge with original
```{r}
imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)

# Frontline <- 
#   full_join(Frontline, imputed_data %>% 
#               select(patientid, starts_with("imp_")), 
#             by = "patientid") 
Frontline_adjusted <- 
  full_join(Frontline_adjusted, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```

@@

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

@@

```{r}
Frontline <- Frontline_adjusted
```

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
<!-- RDI for paclitaxel is not a factor associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059). -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
